Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd
Update Checkpoint3.Rmd
Googele descript

>>>>

`Google Search Interest`
This data set includes two search interest indexes over time, measuring how people in each of the state’s interest in searching either “Kung Flu” or “China Virus” based on the time frame selected in the search. This data is downloaded directly from Google Trends which uses the same technique to track the interest of all searches on the platform. The main downside to this data set is the method of the indexing which makes the comparison from state to state less meaningful since each state is guaranteed to have a 100-level interest on their peak day, and the actual unknown search values can vary greatly across different states.
